\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{textpos}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage{helvet}

\renewcommand{\familydefault}{\sfdefault}
  
  
\setlist[enumerate]{label=\arabic*.,leftmargin=0.8cm}
\setlist[itemize]{label=$\bullet$,leftmargin=0.7cm}
  
\setlength{\TPHorizModule}{\textwidth}
\setlength{\parindent}{0cm}

\setcounter{secnumdepth}{4}

   
\begin{document}

\sloppy


{\Large 

\textbf{Project Description}

\smallskip

[First name  last name, city of all applicants]


\smallskip

[Project title]


\par
}

\medskip

\hrule 

\medskip
\medskip
\medskip
\medskip
\medskip

Sections 1-3 must not exceed 17 pages in total.


\section{Starting point}

State of the art and preliminary work


\section{Objectives and work programme}

\subsection{Anticipated total duration of the project}
\subsection{Objectives}
\subsection{Work programme including proposed research methods}
For each applicant
\subsection{Handling of research data}
\subsection{Relevance of sex, gender and/or diversity}


\section{Project- and subject-related publications}

Works cited from sections 1 and 2, both by the applicant(s) and by third parties. Please include DOI/URL if available. A maximum of ten of your own works cited may be highlighted; font at least Arial 9 pt.


\section{Supplementary information on the research context}

\subsection{Ethical and/or legal aspects of the project}

\subsubsection{General ethical aspects}

[Text]

\subsubsection{Descriptions of proposed investigations involving humans, human materials or identifiable data}

[Text]

\subsubsection{Descriptions of proposed investigations involving experiments on animals}

[Text]

\subsubsection{Descriptions of projects involving genetic resources (or associated traditional knowledge) from a foreign country}

\subsubsection{Explanations regarding any possible safety-related aspects (“Dual Use Research of Concern; foreign trade law)}

\subsection{Employment status information}
For each applicant, state the last name, first name, and employment status (including duration of contract and funding body, if on a fixed-term contract).


\subsection{First-time proposal data}
Only if applicable: Last name, first name of first-time applicant


\subsection{Composition of the project group}
List only those individuals who will work on the project but will not be paid out of the project funds. State each person’s name, academic title, employment status, and type of funding.


\subsection{Researchers in Germany with whom you have agreed to cooperate on this project}


\subsection{Researchers abroad with whom you have agreed to cooperate on this project}

\subsection{Researchers with whom you have collaborated scientifically within the past three years}
This information will help avoid potential conflicts of interest.


\subsection{Project-relevant cooperation with commercial enterprises}
If applicable, please note the EU guidelines on state aid or contact your research institution in this regard.


\subsection{Project-relevant participation in commercial enterprises}
Information on connections between the project and the production branch of the enterprise


\subsection{Scientific equipment}
List larger instruments that will be available to you for the project. These may include large computer facilities if computing capacity will be needed. 


\subsection{Other submissions}
List any funding proposals for this project and/or major instrumentation previously submitted to a third party.


\subsection{Other information}
Please use this section for any additional information you feel is relevant which has not been provided elsewhere.


\section{Requested modules/funds}
Explain each item for each applicant (stating last name, first name).

\subsection{Basic Module}

\subsubsection{Funding for Staff}

\subsubsection{Direct Project Costs}

\paragraph{Equipment up to € 10,000, Software and Consumables}

\paragraph{Travel Expenses}

\paragraph{	Visiting Researchers (excluding Mercator Fellows)}

\paragraph{Expenses for Laboratory Animals}

\paragraph{	Other Costs}

\paragraph{Project-related Publication Expenses}

\subsubsection{Instrumentation}


\paragraph{5.1.3.1	Equipment exceeding € 10,000}

\paragraph{	Major Instrumentation exceeding € 50,000}


\subsection{Module Temporary Position for Principal Investigator}

\subsection{	Module Replacement Funding}

\subsection{	Module Temporary Clinician Substitute}

\subsection{	Module Mercator Fellows}

\subsection{	Module Workshop Funding}

\subsection{	Module Public Relations Funding}

\subsection{ Module Standard Allowance for Gender Equality Measures}
Please detail what measures are planned to promote diversity and equal opportunities.
If you are submitting your proposal for an individual research grant within a network, note that this standard allowance may only be applied for within the coordination project. The coordination project must combine all such requests in its calculation.



\end{document}
